Simulating spaces and stressors

### 2021-01-29 Analysis/01_Simulating_spaces_and_stressors.Rmd
Update 01_Simulating_spaces_and_stressors.Rmd

@@

Adding data in empty spaces

## Equalizing fitness prosseces

>>>>

```{r}
## Removing 50% to flatten the curve
competitive_exclusion <- reduce.space(trait_space,
                                    type = "evenness",
                                    remove = 0.5)
```

```{r}
## Visualising the results
par(mfrow = c(1, 2))
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D null mechanism")
```

## Equalizing fitness processes

```{r}
## Removing 50% to change the trait space size
equalizing_fitness <- reduce.space(trait_space,
                                    type = "size",
                                    remove = 0.5)
```

```{r}
## Visualising the results
par(mfrow = c(1, 2))
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D null mechanism")
```

Adding data in empty spaces (or clumping things together?)

@@
